Kernel k-Groups via Hartigan's Method

### 2018-08-14 energy_clustering/arxiv/energy_clustering.tex
pami/arxiv

\author{Guilherme~Fran\c ca,~Maria L.~Rizzo~and~Joshua T.~Vogelstein
\IEEEcompsocitemizethanks{
\IEEEcompsocthanksitem G. Fran\c ca
is with the Mathematical Institute for Data Science (MINDS), Johns Hopkins
University.\protect \\
E-mail: guifranca@jhu.edu
\IEEEcompsocthanksitem J. T. Vogelstein is 
with the Center for Imaging Science, 
the Department of Biomedical Engineering and Institute for Computational
Medicine, Johns Hopkins University. \protect\\
% note need leading \protect in front of \\ to get a newline within \thanks as
% \\ is fragile and will error, could use \hfil\break instead.
E-mail: jovo@jhu.edu
\IEEEcompsocthanksitem M. L. Rizzo is with the Department of Mathematics
and Statistics, Bowling Green State University. \protect\\
E-mail: mrizzo@bgsu.edu}% <-this % stops an unwanted space
\thanks{Manuscript received August 14, 2018; revised August 14, 2018.}}

% The paper headers
\markboth{Energy Clustering}{}
%{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,clip,keepaspectratio]{gui2.png}}]{Guilherme Fran\c ca} 
has a BS degree in physics and received both his MS and 
PhD in Theoretical Physics from the Institute of 
Theoretical Physics IFT-UNESP/ICTP-SAIFR (2012). He was a Postdoctoral Fellow
with the High Energy Theory group in the Physics Department 
at Cornell University (2013--2015), working on topics of mathematical physics
and non-perturbative methods in quantum field theory 
and statistical mechanics.
He was a Postdoctoral Fellow in
the Computer Science Department at Boston College (2015), working
in optimization methods.
Since 2016 he is a Postdoctoral Fellow at Johns Hopkins University, currently
with the Mathematical Institute for Data Science (MINDS). 
His current research interests involve  
machine learning and optimization.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,clip,keepaspectratio,height=1.30in]{rizzo.jpg}}]{Maria~L.~Rizzo}
holds a BS and MA degree in Mathematics from the University of Toledo, a MS in
Applied Statistics from BGSU, and a PhD from BGSU in 2002. After four years as
Assistant Professor at Ohio University Department of Mathematics, she 
returned to BGSU in 2006, where she is currently Professor of Statistics 
in the Department of
Mathematics and Statistics. Her primary research interests are 
centered on energy
statistics, distance correlation and its applications, computational
statistics, and related topics. In addition to teaching statistics, data
science, and actuarial science, she enjoys writing textbooks about statistical
computing and using R software. She has a forthcoming research 
monograph on energy
statistics (joint with G. Szekely) and also other book writing projects under
contract as well.
\end{IEEEbiography}

% insert where needed to balance the two columns on the last page with
% biographies
%\newpage

\begin{IEEEbiography}[{\includegraphics[width=1in,clip,keepaspectratio]{jovo.png}}]{Joshua~T.~Vogelstein}
received a BS degree from the Department of Biomedical Engineering (BME) at
Washington University in St. Louis, MO in 2002, a MS degree from the
Department of Applied Mathematics and Statistics (AMS) at Johns Hopkins
University (JHU) in Baltimore, MD in 2009, and a PhD degree from the
Department of Neuroscience at JHU in 2009. He was a Postdoctoral Fellow in
AMS/JHU from 2009 until 2011, at which time he was appointed an Assistant
Research Scientist, and became a member of the Institute for Data Intensive
Science and Engineering. He spent 2 years at Information Initiative at Duke
University, before coming home to his current appointment as 
Assistant Professor
in BME/JHU, and core faculty in both the Institute for Computational Medicine
and the Center for Imaging Science, as well as a member of the Kavli
Neuroscience Discovery Institute. He married his kindergarten sweetheart in the
summer of 2014.

His primary research interest is to extend and fuse statistical 
machine learning
and big data science to address the most important brain science and mental
health questions of our time, particularly  connectomics. 
His group’s research
has been featured in a number of prominent scientific and engineering journals
and conferences including Nature, Nature Methods, Science, Cell, PNAS, Science
Translational Medicine, JMLR, PAMI, Annals of Applied Statistics,  NIPS, and
SIAM Journal of Matrix Analysis and Applications. In 2011, he co-founded the
Open Connectome Project which expanded in 2015 to be NeuroData, whose mission
is to enable terascale neuroscience for everyone. All his works are conducted
according to the highest standards of open science.
\end{IEEEbiography}

>>>>

\author{Guilherme~Fran\c ca,~Maria L.~Rizzo~and~Joshua T.~Vogelstein
\IEEEcompsocitemizethanks{
\IEEEcompsocthanksitem G. Fran\c ca
is with the Mathematical Institute for Data Science (MINDS), Johns Hopkins
University.\protect \\
E-mail: guifranca@jhu.edu
\IEEEcompsocthanksitem J. T. Vogelstein is 
with the Center for Imaging Science, 
the Department of Biomedical Engineering and Institute for Computational
Medicine, Johns Hopkins University. \protect\\
% note need leading \protect in front of \\ to get a newline within \thanks as
% \\ is fragile and will error, could use \hfil\break instead.
E-mail: jovo@jhu.edu
\IEEEcompsocthanksitem M. L. Rizzo is with the Department of Mathematics
and Statistics, Bowling Green State University. \protect\\
E-mail: mrizzo@bgsu.edu}% <-this % stops an unwanted space
%\thanks{Manuscript received August 14, 2018; revised August 14, 2018.}
}

% The paper headers
%\markboth{Energy Clustering}{}
%{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%

@@

%\begin{IEEEbiography}[{\includegraphics[width=1in,clip,keepaspectratio]{gui2.png}}]{Guilherme Fran\c ca} 
%has a BS degree in physics and received both his MS and 
%PhD in Theoretical Physics from the Institute of 
%Theoretical Physics IFT-UNESP/ICTP-SAIFR (2012). He was a Postdoctoral Fellow
%with the High Energy Theory group in the Physics Department 
%at Cornell University (2013--2015), working on topics of mathematical physics
%and non-perturbative methods in quantum field theory 
%and statistical mechanics.
%He was a Postdoctoral Fellow in
%the Computer Science Department at Boston College (2015), working
%in optimization methods.
%Since 2016 he is a Postdoctoral Fellow at Johns Hopkins University, currently
%with the Mathematical Institute for Data Science (MINDS). 
%His current research interests involve  
%machine learning and optimization.
%\end{IEEEbiography}
%
%\begin{IEEEbiography}[{\includegraphics[width=1in,clip,keepaspectratio,height=1.30in]{rizzo.jpg}}]{Maria~L.~Rizzo}
%holds a BS and MA degree in Mathematics from the University of Toledo, a MS in
%Applied Statistics from BGSU, and a PhD from BGSU in 2002. After four years as
%Assistant Professor at Ohio University Department of Mathematics, she 
%returned to BGSU in 2006, where she is currently Professor of Statistics 
%in the Department of
%Mathematics and Statistics. Her primary research interests are 
%centered on energy
%statistics, distance correlation and its applications, computational
%statistics, and related topics. In addition to teaching statistics, data
%science, and actuarial science, she enjoys writing textbooks about statistical
%computing and using R software. She has a forthcoming research 
%monograph on energy
%statistics (joint with G. Szekely) and also other book writing projects under
%contract as well.
%\end{IEEEbiography}
%
%
%% insert where needed to balance the two columns on the last page with
%% biographies
%%\newpage
%
%\begin{IEEEbiography}[{\includegraphics[width=1in,clip,keepaspectratio]{jovo.png}}]{Joshua~T.~Vogelstein}
%received a BS degree from the Department of Biomedical Engineering (BME) at
%Washington University in St. Louis, MO in 2002, a MS degree from the
%Department of Applied Mathematics and Statistics (AMS) at Johns Hopkins
%University (JHU) in Baltimore, MD in 2009, and a PhD degree from the
%Department of Neuroscience at JHU in 2009. He was a Postdoctoral Fellow in
%AMS/JHU from 2009 until 2011, at which time he was appointed an Assistant
%Research Scientist, and became a member of the Institute for Data Intensive
%Science and Engineering. He spent 2 years at Information Initiative at Duke
%University, before coming home to his current appointment as 
%Assistant Professor
%in BME/JHU, and core faculty in both the Institute for Computational Medicine
%and the Center for Imaging Science, as well as a member of the Kavli
%Neuroscience Discovery Institute. He married his kindergarten sweetheart in the
%summer of 2014. 
%
%His primary research interest is to extend and fuse statistical 
%machine learning
%and big data science to address the most important brain science and mental
%health questions of our time, particularly  connectomics. 
%His group’s research
%has been featured in a number of prominent scientific and engineering journals
%and conferences including Nature, Nature Methods, Science, Cell, PNAS, Science
%Translational Medicine, JMLR, PAMI, Annals of Applied Statistics,  NIPS, and
%SIAM Journal of Matrix Analysis and Applications. In 2011, he co-founded the
%Open Connectome Project which expanded in 2015 to be NeuroData, whose mission
%is to enable terascale neuroscience for everyone. All his works are conducted
%according to the highest standards of open science.
%\end{IEEEbiography}
